Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-16 paper/abstract.tex
pass on abstract and intro

JavaScript is a popular programming language today. Several engine
implementations compete for market dominance. Although a specification
and a conformance test suite exist to guide engine development, bugs
occur and have important consequences given the language
popularity. One reason for the difficulty in implementing correct
engines stems from the fact that the specification is incomplete and
evolves frequently.

This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on this domain. For that, we explored two
simple diversity-aware methods---test transplantation and cross-engine
differential testing. Test transplantation evaluates the effects of
running test suites of a given engine in another engine. Cross-engine
differential testing evaluates the effects of fuzzing existing inputs
and then comparing the output produced by different engines with a
differential oracle.

>>>>

JavaScript is a popular programming language today. Several engine
implementations compete for market dominance. Although specification
and conformance test suite exist to guide engine development, bugs
occur and have important consequences given the language
popularity. One reason for the difficulty in implementing correct
engines stems from the fact that the specification is incomplete and
evolves frequently.

This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. For that, we explored two
simple diversity-aware methods---test transplantation and cross-engine
differential testing. Test transplantation evaluates the effects of
running test suites of a given engine in another engine. Cross-engine
differential testing evaluates the effects of fuzzing existing inputs
and then comparing the output produced by different engines with a
differential oracle.

### 2018-08-16 paper/paper.tex
pass on abstract and intro

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with significant
penetration in various segments including, web development, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification
and implementations. It is natural to expect that such improvements
lead to sensible implementation changes. Even small changes can have
high practical impact. For example, in October 2014 a new attribute
added to Array objects resulted in the MS Outlook Calendar web app
stop working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
Intuitively, developing reliable engines is difficult because
specifications are incomplete and evolve frequently.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
a test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} relates features of \js\ with the engines that
support them. To sum, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason making test
automation more challenging.

@@

%% WHAT WE DID
The goal of this paper is to assess reliability of popular
\js\ engines. The paper reports the results of a study that evaluates
the effectiveness of two complementary diversity-aware testing techniques. \emph{Test transplantation} leverages
diversity of test cases to find bugs. It evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that developers design test cases
differently; hence replaying the test in a different engine may reveal
unanticipated problems. \emph{Cross-engine differential testing}
evaluates the ability of leveraging diversity of engine
implementations to find bugs. More precisely, it fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files\footnote{These files are created with the grammar-based fuzzer
  jsfunfuzz~\cite{jsfunfuzz}. Look for option ``compare\_jit'' from funfuzz.} against different configurations of their
\smonkey{} engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning} as opposed to different builds of the
same engine. This approach has not been
popularized, certainly, because it is still not practical to fully automate--a
number of legitimate reasons exist, other than a bug, for a test
execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.

%% WHAT WE FOUND
To sum, we found that \Fix{...}

%% LIST OF CONTRIBUTIONS
This paper makes the following contributions \Fix{...}

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity, which is specially rich in this
domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the Test262 standard
conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we hope that that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms such as those that
could emerge from implementation-dependent behavior. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typically make valid
changes only in literals of the language could expose important
bugs. All in all, we want to assess the impact of simple approaches
that leverage on diversity to find bugs in \js\ engines with the goal
of assessing their reliability.

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   16 & 8/08  & V8 & \textbf{Assigned} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table*}

Figure~\ref{tab:test-transplantation-bugs} lists all bugs we found
with test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the corresponding
post in the bug tracking system where the discussion thread with
engine developers can be found (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, it is important to note that
\jsc{} uses five different severity levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
use only two. As usual, the smallest the severity value the highest
the severity of the bug. We use a dash (``-'') as the severity level
for bugs with pending confirmation.

>>>>

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with penetration in
various segments including, web development, mobile, and, more
recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
interest of the community for the language encourages constant
improvements in its specification and implementations. It is natural
to expect that such improvements lead to sensible changes in engine
implementation. Even small changes can have high practical impact. For
example, in October 2014 a new attribute added to Array objects
resulted in the MS Outlook Calendar web app stop working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
Intuitively, developing reliable engines is difficult because
specifications are incomplete and evolve frequently.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
a test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} relates \js\ features with the engines that
support them. To sum, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason making test
automation more challenging.

@@

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases differently; hence
replaying the test in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} evaluates the
ability of leveraging diversity of engine implementations to find
bugs. More precisely, it fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug.

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). In that setting, test outcomes are
expected to be identical. Mozilla uses this approach since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
popularized to similar extent. One possible reason is that it is still
not practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Table~\ref{tab:false-positives}). Recently, Patra and
Pradel~\cite{patra2016learning} explored the idea. They proposed a
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. Their main contribution is analytical whereas our main
contribution is empirical--goal is to evaluate ability and cost of
simple diversity-aware approaches to find bugs in \js\ engines.

\emph{Results.}~\Fix{REVISE}We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (\noBugsTransplantationConfirmed{} confirmed) and differential
testing revealed \noBugsDifferentialTesting{} bugs
(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
that most of these bugs affected only two engines--Apple's \jsc{}
(\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found only
one bug in Google \veight{} and none in Mozilla's \smonkey{}. Although
our experience indicates that more research needs be done to automate
parts of the inspection process, our results show that exploring
diversity is a valuable help to find bugs in JavaScript engines.

%% LIST OF CONTRIBUTIONS
This paper makes the following contributions.
\begin{itemize}
  \item We ran a comprehensive study to analyze the effectiveness of
    simple diversity-aware techniques to find bugs in highly-popular
    \js\ engines.

  \item We reported more than \Fix{50} bugs on these engines over a
    period of 5 months.

  \item We offered insights on how to reduce cost of analyzing
    warnings reported by diversity-aware techniques and make the
    approach more practical.

  \item We made our testing infrastructure, results, and experimental
    scripts available to the public. (upon request for anonimity.)
\end{itemize}

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity, which is specially rich in this
domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the Test262 standard
conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we conjecture that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typically make valid
changes only in literals of the language could expose important
bugs. All in all, we want to assess the impact of practical approaches
that leverage diversity to find bugs in \js\ engines.

@@

\begin{table}[t!]
\setlength{\tabcolsep}{2pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   16 & 8/08  & V8 & \textbf{Assigned} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found
with test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the corresponding
post in the bug tracking system where the discussion thread with
engine developers can be found (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, it is important to note that
\jsc{} uses five different severity levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
use only two. As usual, the smallest the severity value the highest
the severity of the bug. We use a dash (``-'') as the severity level
for bugs with pending confirmation.
